### 2014-06-01 ACL2014/system.tex
section 3 edits

In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop). 
In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implmentation scales to hundreds of millions of queries.

\begin{figure}
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}(q), i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

\subsection{Reusing Hash Functions}
\label{subsec:resuseHash}
In Section \ref{subsec:vlsh:cosine}, we showed that vanilla \lsh requires $L\times K$ hash functions. 
However generating hash functions is computationally expensive as 
it takes time to read all features and 
evaluate hash functions over all those features to generate a single bit. 
To minimize the number of hash functions computations, 
we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
in which hash functions are reused to generate $L$ tables. $K$ is assumed to be even and $R \approx	\sqrt L$. 
We generate $f(q)=(h_1(q),h_2(q),\dots,h_{K/2}(q)))$ of length $k/2$. 
Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. Using such pairing, we
can thus generate $L= \frac{R (R -1)}{2}$ hash indices. 
This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).    
For rest of this paper, we use the above trick to generate $L$ hash tables with bucket indices of width $K$ bits.  
\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{ll}
\hline
\hline
 \textbf{Symbol} &  \textbf{Description} \\
\hline 
$N$ & \# of query terms \\
$D$ & \# of features i.e. all clicked unique urls \\
\hline
\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
	 & to generate the index of a table \\
\hline
 \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
\hline
$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
$\tau$ & $\tau$ threshold \\
Recall & fraction of similar candidates retrieved \\
Comparisons & Avg \# of pairwise comparisons per query  \\
\hline 
\end{tabular}
\caption{\footnotesize{Major Notations}}
}
\label{tab:notation}
\end{table}

>>>>

In this work, we have implemented the above algorithm in a map-reduce setting (Hadoop). 
In Section \ref{subsec:eval:vanillaLSH}, we show that the map-reduce implementation scales to hundreds of millions of queries.

\begin{figure}
\fbox{
\begin{minipage}{2.5in}
{\bf Preprocessing:} Input is $N$ queries with their respective feature vectors.
\begin{itemize}
\item Select $L$ functions $g_j$, $j=1,2,\dots,L$, setting  $g_j(q)=(h_{1,j}(q),h_{2,j}(q),\dots,h_{K,j}(q))$, where 
$\{h_{i,j}, i\in [1, K], j\in [1,L]\}$ are chosen at random from the \lsh family.
\item Construct $L$ hash tables, $\forall 1 \leq j \leq  L$. 
All queries with similar $g_j$ functions ($\forall 1 \leq j \leq  L$) are placed in the same bucket.    
\end{itemize}

@@

\subsection{Reusing Hash Functions}
\label{subsec:resuseHash}
In Section \ref{subsec:vlsh:cosine}, we showed that vanilla \lsh requires $L\times K$ hash functions. 
However generating hash functions is computationally expensive as 
it takes time to read all features and 
evaluate hash functions over all those features to generate a single bit. 
To minimize the number of hash functions computations, 
we use a trick from Andoni and Indyk \shortcite{Andoni08CACM} 
in which hash functions are reused to generate $L$ tables. $K$ is assumed to be even and $R \approx	\sqrt L$. 
We generate $f(q)=(h_1(q),h_2(q),\dots,h_{K/2}(q)))$ of length $k/2$. 
Next, we define $g(q)=(f_a,f_b)$, where $1\leq a < b \leq R$. Using such pairing, we
can thus generate $L= \frac{R (R -1)}{2}$ hash indices. 
This scheme requires O($K  \sqrt L$) hash functions, instead of O($KL$).    
For rest of this paper, we use the above trick to generate $L$ hash tables with bucket indices of width $K$ bits.  
\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{ll}
\hline
\hline
 \textbf{Symbol} &  \textbf{Description} \\
\hline 
$N$ & \# of query terms \\
$D$ & \# of features i.e. all clicked unique urls \\
\hline
\multirow{3}{*}{$K$} & \# of hash functions concatenated together \\ 
   & $g(q)=(h_1(q),h_2(q),\dots,h_k(q)))$ \\ 
	 & to generate the index of a table \\
\hline
 \multirow{2}{*}{$L$} & \# of tables generated independently \\ 
	  &  with $g_j(q)$ index, $\forall 1 \leq j \leq  L$  \\
\hline
$F$ & \# of bits flipped, $\forall 1 \leq j \leq  L$   \\
$\tau$ & $\tau$ threshold \\
Recall & fraction of similar candidates retrieved \\
Comparisons & Avg \# of pairwise comparisons per query  \\
\hline 
\end{tabular}
\caption{\footnotesize{Major Notations}}

\label{tab:notation}
\end{table}
